Supplemental Material: Multidimensional analysis and detection of informative features in human brain white matter

### 2021-04-20 reports/manuscript/supplemental.tex
ENH: Add responses to reviewer comments

Here, we present the bundle profiles and $\hat{\beta}$ coefficients
for each dataset. Throughout this section, diffusion metrics are plotted
along the length of eighteen bundles:
right corticospinal (CSTR),
left corticospinal (CSTL),
right uncinate (UNCR),
left uncinate (UNCL),
left inferior fronto-occipital fasciculus (IFOL),
right inferior fronto-occipital fasciculus (IFOR),
right arcuate (ARCR),
left arcuate (ARCL),
right thalamic radiation (ATRR),
left thalamic radiation (ATRL),
right cingulum cingulate (CGCR),
left cingulum cingulate (CGCL),
callosum forceps major (CFP),
callosum forceps minor (CFA),
right inferior longitudinal fasciculus (ILFR),
left inferior longitudinal fasciculus (ILFL),
right superior longitudinal fasciculus (SLFR),
and left superior longitudinal fasciculus (SLFL).
We display results for two different diffusion metrics: fractional anisotropy
(FA) and mean diffusivity (MD), which are extracted from different diffusion
models depending on the dataset: diffusion tensor imaging (DTI) for the ALS
and WH datasets and diffusion kurtosis imaging (DKI) for the HBN and Cam-CAN
datasets \cite{jensen2005diffusion}. The diffusion metric is always plotted
on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on
the twin axis on the right-hand-side. The scale of the $\hat{\beta}$-axis is
shared between the FA and MD metrics so that one can compare the relative
imporance of each metric.

>>>>

Here, we present the bundle profiles and $\hat{\beta}$ coefficients
for each dataset. Throughout this section, diffusion metrics are plotted
along the length of eighteen bundles:
right corticospinal (CSTR),
left corticospinal (CSTL),
right uncinate (UNCR),
left uncinate (UNCL),
left inferior fronto-occipital fasciculus (IFOL),
right inferior fronto-occipital fasciculus (IFOR),
right arcuate (ARCR),
left arcuate (ARCL),
right thalamic radiation (ATRR),
left thalamic radiation (ATRL),
right cingulum cingulate (CGCR),
left cingulum cingulate (CGCL),
callosum forceps posterior (CFP),
callosum forceps anterior (CFA),
right inferior longitudinal fasciculus (ILFR),
left inferior longitudinal fasciculus (ILFL),
right superior longitudinal fasciculus (SLFR),
and left superior longitudinal fasciculus (SLFL).
We display results for two different diffusion metrics: fractional anisotropy
(FA) and mean diffusivity (MD), which are extracted from different diffusion
models depending on the dataset: diffusion tensor imaging (DTI) for the ALS
and WH datasets and diffusion kurtosis imaging (DKI) for the HBN and Cam-CAN
datasets \cite{jensen2005diffusion}. The diffusion metric is always plotted
on the left $y$-axis while the $\hat{\beta}$ coefficients are displayed on
the twin axis on the right-hand-side. The scale of the $\hat{\beta}$-axis is
shared between the FA and MD metrics so that one can compare the relative
imporance of each metric.
